---
title: "Web"
runtime: shiny
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
```{r}
library(ISwR)
library(TTR)
library(readr)

A2010 <- read.csv("BP Apprehensions 2010.csv", header = TRUE, stringsAsFactors = FALSE)
A2017 <- read.csv("PB Apprehensions 2017.csv", header = TRUE, stringsAsFactors = FALSE)
yearA <- as.data.frame(matrix(c(rowSums(A2010[,-1])),nrow = 1))
colnames(yearA) <- A2010[,1]
yearB<- as.data.frame(matrix(c(rowSums(A2017[,-1])),nrow = 1))
colnames(yearB) <- A2010[,1]
yearAB <- rbind(yearA, yearB)
row.names(yearAB) <- c("year2010", "year2017")



#Compare by month
yearA1 <- as.data.frame(matrix(c(colSums(A2010[,-1])),nrow = 1))

colnames(yearA1) <- c(10:12,1:9)

yearB1<- as.data.frame(matrix(c(colSums(A2017[,-1])),nrow = 1))

colnames(yearB1) <- c(10:12,1:9)

yearAB1 <- rbind(yearA1, yearB1)

row.names(yearAB1) <- c("year2010", "year2017")
```



```{r}
library(shiny)

# Define UI for dataset viewer app ----
ui <- fluidPage(

  # App title ----
  titlePanel("Group project"),

  # Sidebar layout with input and output definitions ----
  sidebarLayout(

    # Sidebar panel for inputs ----
    sidebarPanel(

      # Input: Select a dataset ----
      selectInput("dataset", "Choose a graph to view:",
                  choices = c("By sector", "By month", "Time series")),
    
      actionButton("update", "Update View")


    ),

    # Main panel for displaying outputs ----
    mainPanel(

      h4("Graph"),
      plotOutput("graph")
      
    )

  )
)

# Define server logic to summarize and view selected dataset ----
server <- function(input, output) {

  # Return the requested dataset ----
  # Note that we use eventReactive() here, which depends on
  # input$update (the action button), so that the output is only
  # updated when the user clicks the button
  datasetInput <- eventReactive(input$update, {
    switch(input$dataset,
           "By sector" = "sector",
           "By month" = "month",
           "Time series" = "ts")
  }, ignoreNULL = FALSE)

  testInput <- eventReactive(input$update, {
    switch(input$test,
           "T-test1" = "1",
           "T-test2" = "2",
           "Three months compare" = "3")
  }, ignoreNULL = FALSE)
  
  
  output$graph <- renderPlot({
    choice <- datasetInput()
    if (choice == "sector"){
      barplot(as.matrix(yearAB), beside = TRUE, col = c("red", "blue"), bty="n" )

legend("topleft", c("year2010","year2017"), pch=15,  col=c("red","blue"),  bty="n")

    }
    if (choice == "month"){
         barplot(as.matrix(yearAB1), beside = TRUE, col = c("red", "blue"), bty="n" )

legend("topleft", c("year2010","year2017"), pch=15,  col=c("red","blue"),  bty="n")
    }
    if (choice == "ts"){
ts1 <- read_csv("NEW PB monthly summaries.csv", col_names = FALSE)
ts2 <- as.vector(t(ts1))
ts2 <- rev(ts2)
ts3 <- ts(ts2, start = c(2000,10), frequency=12)
x <- 2000.5
y <- rev(rowMeans(ts1))
          ts.plot(ts3, gpars=list(xlab="year", ylab="Apprehensions", lty=1))
for(i in 1:18){
    segments(x,y[i],x+1,y[i],col = 'red')
    text(x+1.5,y[i],as.character(x-.5),col = 'red',cex = 0.5)
    x <- x+1
}
    }
  })
}

# Create Shiny app ----
shinyApp(ui, server)
```

##T-test 1
```{r}
a<-as.numeric(which.max(yearA))
b<-as.numeric(which.max(yearB))
t.test(as.numeric(A2010[a,-1]), as.numeric(A2017[b,-1]), paired = FALSE)
```

Assume 95% confidence level, the p-value 0.06346 is bigger than 0.05,
So, we do not reject H0 which states there is no change in the means
of the most apprehension sectors of 2010 and 2017. In conclusion, we
are 95% confident to say that there is a change between two means.


##Find the three months with most apprehension of 2010 and 2017
```{r}
sum2010 <- runSum(as.numeric(yearA1),n = 3, cumulative = FALSE)
sum2017 <- runSum(as.numeric(yearB1),n = 3, cumulative = FALSE)
max(sum2010,na.rm = T)
max(sum2017,na.rm = T)
which.max(sum2010)
which.max(sum2017)
```



The three months period with the most apprehension of 2010 is March,April, and May, with the sum 163643. 
The three months period with the most apprehension of 2017 is October,November, and December, with the sum 136646.
The sum of 2010 is bigger than the sum of 2017


##T-test 2
```{r}

yearA2<-yearA1[(which.max(sum2010)-2):which.max(sum2010)]
yearB2<-yearB1[(which.max(sum2017)-2):which.max(sum2017)]
t.test(as.numeric(yearA2),as.numeric(yearB2), paired = FALSE)
```

Assuming 95% confidence level, the p-value is 0.1541 is bigger than 0.05, So we do not reject H0 which states there is no change in the sums of three months with the most apprehension of 2010 and 2017. In conclusion, we are 95% confident to say that there is a change between two group of sums. 


